---
title: "slvwagner"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{slvwagner}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(slvwagner)
```

My R library, including all functions I use very often.

Some function need yacas a symbolic solver: \
http://www.yacas.org/

## Content

### Geometrical stuff 
Functions start with geo_

-   Conic section 
-   Slerp 
-   Intersection of sphere and line, 
-   Intersecting point(s) of plane and line
-   Convert plane equation (coordinate form) into parametric from. Get position vector and tow orientation vectors.  
-   Intersection point from three globs upon an initial guess

### Math 
Functions start with math_

-   Transformation from spherical to Cartesian coordinate system and back. 
-   Rotation Matrix in R and Ryacas (YACAS)
-   lf Linear function helpers 
-   Quadrant and angle finder for 2D vector
-   cross and dot vector product
-   Magnitude of vector 
-   In-between angel of two vectors
-   Get polynomial from roots 
-   Round polynomial equation
-   Generate non linear Vector with start, end and vector length

### Math in yacas 
Functions start with yac_

  -   Rotation matrix 2D
  -   Rotation matrix 3D

#### Linear function helper
Functions start with lf_

-   Simple linear function 
-   perpendicular to function 
-   Intersection point of two functions
-   Linear function from two points

#### signal
Functions start with signal_

-   To average a signal around zero (AC coupling)

### find 
Functions start with find_

-   find_edges2D in evenly spaced gird
-   find_edges3D in evenly spaced gird

```{r}
n_col <- 7
n_row <- 4

c_search <- c(
  0,1,0,0,0,1,0,
  1,1,1,1,1,1,1,
  0,1,0,1,1,1,1,
  0,0,1,1,1,1,1
  )

m_grid <- expand.grid(x = 0:(n_col-1), y = 0:(n_row-1))|>
  as.matrix()|>
  cbind(c_search)

m_grid <- cbind(m_grid,
                edge = find_edges_2D(m_grid[,"c_search"], n_col))
```


```{r echo=FALSE}
m_grid|>
  plot(col = m_grid[,"c_search"],
       xlim=c(0,n_col-1), ylim=c(0,n_row-1),
       # asp = 1,
       pch = 19,
       cex = 1.,
       main = "Input: c_search")

m_grid|>
  plot(col = m_grid[,"edge"],
       xlim=c(0,n_col-1), ylim=c(0,n_row-1),
       # asp = 1,
       pch = 19,
       cex = 1.,
       main = "Edge")

```


#### statistical 
Functions start with stat_

-   Process capability index (CPK)
-   Probability density function

### business
-   NPS (net promoter score)

### Utilities

#### Plot
Functions start with plot_

-    Get normal distributed overlay for faceted histograms

#### System 
Functions start with r_

-   r_ R utility functions, e.g. windows path to R compatible path

#### Fast dictionary
Function start with dict_

-   Create fast dictionary, convenience functions.

